s.function

### 2025-01-23 src/s_la_per_firm_corrected.Rmd
late

  filter(abs(diff_1st) > 253 & rank > 100 & q == "95") %>% distinct(LAD21NM)

@@

  geom_text_repel(aes(x = Inf, label = label), 
                  size = 3, hjust = 0, color = "darkorange3", 
                  max.overlaps = Inf,
                  min.segment.length = Inf,
                  hjust = "left") + # x = 2012 + .1

  geom_text_repel(aes(x = -Inf, label = label.low), 
                  size = 3, hjust = 0, color = "darkorchid4", 
                  max.overlaps = Inf,
                  min.segment.length = Inf,
                  hjust = "left") + # x = 2012 + .1

@@

@@

>>>>

  #filter(abs(diff_1st) > 253 & rank > 100 & q == "95") %>% distinct(LAD21NM)

@@

  # geom_text_repel(aes(x = Inf, label = label), 
  #                 size = 3, hjust = 0, color = "darkorange3", 
  #                 max.overlaps = Inf,
  #                 min.segment.length = Inf,
  #                 hjust = "left") + # x = 2012 + .1
  # 
  # geom_text_repel(aes(x = -Inf, label = label.low), 
  #                 size = 3, hjust = 0, color = "darkorchid4", 
  #                 max.overlaps = Inf,
  #                 min.segment.length = Inf,
  #                 hjust = "left") + # x = 2012 + .1

@@

## Table for leapfroging

@@

path.out <- paste0(path, "/outputs/ranks/late.csv")
write_csv(late, path.out)
